Demonstration of matching route networks

### 2024-01-29 r/README.qmd
Add minimal example with plausible result

```{r}
x = sf::read_sf("data-raw/geojson/princes_street_minimal.geojson")
y = sf::read_sf("data-raw/geojson/princes_street_minimal_x_1.geojson")
```

@@

>>>>

```{r}
x = sf::read_sf("data-raw/geojson/princes_street_minimal_x_1.geojson")
x = x |> sf::st_transform("EPSG:27700")
y = sf::read_sf("data-raw/geojson/princes_street_minimal.geojson")
y = y |> sf::st_transform("EPSG:27700")
```

@@

```{r}
x_joined_df = rnet_match(x, y, dist_tolerance = 20, slope_tolerance = 0.1, trees = "xy")
x_aggregated_x = x_joined_df |>
  group_by(j) |>
  mutate(ij = y$value * shared_len) |>
  group_by(j) |>
  summarise(value = sum(ij))

```

```{r}
```
